Interpreting Random Forest Predictions for Firearm Identification Using LIME

### 2019-02-07 papers/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
finished moving training and testing data cleaning steps to journal 01

```{r}
# Obtain features used when fitting the rtrees random forest
rf_features <- rownames(rtrees$importance)

# Add the random forest score to the training set
# hamby173and252_train$rfscore = predict(rtrees,
#                                        hamby173and252_train %>% select(rf_features),
#                                        type = "prob")[,2]
# 
# Save the adjusted training data
# write.csv(hamby173and252_train %>% select(-X), "../data/hamby173and252_train.csv",
#           row.names = FALSE)
```

@@

```{r}
# Load in the Hamby 224 datasets
hamby224_set1 <- readRDS("../data/h224-set1-features.rds")
hamby224_set11 <- readRDS("../data/h224-set11-features.rds")
```

```{r}
# If the test data does not exist, clean the data, create the test data, and save it
# Otherwise, load in the test data
if(!file.exists("../data/hamby224_test.csv")) {

  # Clean the Hamby 224 set 1 data
  hamby224_set1_cleaned <- hamby224_set1 %>%
    select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
    rename(bullet1 = bulletA,
           bullet2 = bulletB, 
           land1 = landA,
           land2 = landB) %>%
    mutate(study = factor("Hamby 224"), 
           set = factor("Set 1"),
           bullet1 = recode(factor(bullet1), 
                            "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
           bullet2 = recode(factor(bullet2), 
                            "1" = "Known 1", "2" = "Known 2", "Q" = "Questioned"),
           land1 = recode(factor(land1), 
                          "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
                          "4" = "Land 4", "5" = "Land 5", "6" = "Land 6"),
           land2 = recode(factor(land2), 
                          "1" = "Land 1", "2" = "Land 2", "3" = "Land 3", 
                          "4" = "Land 4", "5" = "Land 5", "6" = "Land 6")) %>%
    select(study, set, bullet1:land2, rf_features, rfscore, samesource)

  # Clean the Hamby 224 set 11 data
  hamby224_set11_cleaned <- hamby224_set11 %>%
    select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
    rename(bullet1 = bulletA,
           bullet2 = bulletB, 
           land1 = landA,
           land2 = landB) %>%
    mutate(study = factor("Hamby 224"), 
           set = factor("Set 11"),
           bullet1 = recode(factor(bullet1), 
                            "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
                            "Bullet I" = "Questioned"),
           bullet2 = recode(factor(bullet2), 
                            "Bullet 1" = "Known 1", "Bullet 2" = "Known 2", 
                            "Bullet I" = "Questioned")) %>%
    select(study, set, bullet1:land2, rf_features, rfscore, samesource)

  # Create a dataset with all combinations of lands and bullets comparisons for each set
  combinations <- data.frame(set = factor(rep(c("Set 1", "Set 11"), each = 324)),
                      expand.grid(land1 = factor(c("Land 1", "Land 2", "Land 3", 
                                                   "Land 4", "Land 5", "Land 6")),
                                  land2 = factor(c("Land 1", "Land 2", "Land 3", 
                                                   "Land 4", "Land 5", "Land 6")),
                                  bullet1 = factor(c("Known 1", "Known 2", "Questioned")),
                                  bullet2 = factor(c("Known 1", "Known 2", "Questioned"))))

  # Join the two cleaned Hamby 224 sets into one testing set
  hamby224_test <- suppressWarnings(bind_rows(hamby224_set1_cleaned,
                                              hamby224_set11_cleaned)) %>%
    mutate(set = factor(set),
           bullet1 = factor(bullet1),
           bullet2 = factor(bullet2),
           land1 = factor(land1),
           land2 = factor(land2)) %>%
    right_join(combinations, by = c("set", "land1", "land2", "bullet1", "bullet2")) %>%
    filter(!(bullet1 == "Questioned" & bullet2 == "Known 1"),
           !(bullet1 == "Questioned" & bullet2 == "Known 2"),
           !(bullet1 == "Known 2" & bullet2 == "Known 1")) %>%
    arrange(rfscore) %>%
    mutate(case = factor(1:length(study))) %>%
    select(case, study:samesource)

  # Save the test data as a .csv file
  write.csv(hamby224_test, "../data/hamby224_test.csv", row.names = FALSE)

  # Read in the test data
  hamby224_test <- read.csv("../data/hamby224_test.csv")

@@

>>>>

@@

```{r}
# Read in the test data
hamby224_test <- read.csv("../data/hamby224_test.csv")
```

@@

```{r}
# Obtain features used when fitting the rtrees random forest
rf_features <- rownames(rtrees$importance)
```
